Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-10 intro.tex
more tweaks

The rest of the paper is organized as follows:
Section~\ref{sec:related} discusses previous results on [[what]] and
[[what]] and situates this work in that
context. Section~\ref{sec:methods} covers the experimental setup and
methods used to collect each time series. Section~\ref{sec:model}
describes the prediction models we implemented.  In
Section~\ref{sec:meaComplex}, we review weighted permutation entropy.
In Section~\ref{sec:results}, we estimate the complexity of each time
series and compare that complexity to the accuracy of predictions
produced by the methods of Section~\ref{sec:model} on that time
series.  In Section~\ref{sec:conc}, we discuss these results and their
implications and consider future areas of research.

>>>>

The rest of the paper is organized as follows:
Section~\ref{sec:related} discusses previous results on generating partitions, local modeling, and error distribution analysis, and situates this work in that
context. Section~\ref{sec:methods} covers the experimental setup and
methods used to collect each time series. Section~\ref{sec:model}
describes the prediction models we implemented.  In
Section~\ref{sec:meaComplex}, we review weighted permutation entropy.
In Section~\ref{sec:results}, we estimate the complexity of each time
series and compare that complexity to the accuracy of predictions
produced by the methods of Section~\ref{sec:model} on that time
series.  In Section~\ref{sec:conc}, we discuss these results and their
implications and consider future areas of research.
